\documentclass{article}

% ---------------------------------------------------------
% GLOBAL SETTINGS
% ---------------------------------------------------------

% Icons
\usepackage{fontawesome}

% Page geometry
\usepackage{geometry}
\geometry{
  a4paper,
  left=20mm,
  top=20mm,
  right=20mm,
}

% Additional commands for spacing
\usepackage{setspace}

% Links
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
}

% List customization
\renewcommand\labelitemi{---}
\usepackage{enumitem}

% Table customization
\setlength{\tabcolsep}{0ex}

% Header/Footer customization.
\usepackage{fancyhdr}

% ---------------------------------------------------------
% COMMANDS
% ---------------------------------------------------------

% Title
\newcommand*{\applicant}[1]{\gdef\applicanttext{#1}}
\newcommand*{\github}[1]{\gdef\githubtext{#1}}
\newcommand*{\email}[1]{\gdef\emailtext{#1}}
\newcommand*{\skype}[1]{\gdef\skypetext{#1}}
\newcommand*{\linkedin}[1]{\gdef\linkedintext{#1}}
\newcommand*{\location}[1]{\gdef\locationtext{#1}}
\newcommand*{\phone}[1]{\gdef\phonetext{#1}}

\renewcommand\maketitle{
  {\setstretch{1.2}
    \centerline{
       \textbf{\huge{\expandafter\MakeUppercase\expandafter{\applicanttext}}}
    }
    \begin{center}
      \ifdefined\emailtext
        \faEnvelopeO \hspace{0.1cm} \emailtext \hspace{0.1cm}
      \fi
      \ifdefined\githubtext
        \faGithub \hspace{0.1cm} \githubtext \hspace{0.1cm}
      \fi
      \ifdefined\skypetext
        \faSkype \hspace{0.1cm} \skypetext \hspace{0.1cm}

      \fi
      \ifdefined\linkedintext
        \faLinkedin \hspace{0.1cm} \linkedintext

      \fi
    \end{center}

    \begin{center}
      \ifdefined\locationtext
        \faHome \hspace{0.1cm} \locationtext \hspace{0.1cm}
      \fi
      \ifdefined\phonetext
        \faMobile \hspace{0.1cm} \phonetext \hspace{0.1cm}

      \fi
    \end{center}
  }
}

% Section
\newcommand{\cvsection}[1]{
  \vspace{2.6ex}
  \noindent\textbf{\large{\uppercase{#1}}}
  \vspace{1ex}
  \hrule
  \vspace{1.5ex}
}

% Paragraph header
\newcommand{\cvparagraph}[3]{
  \noindent\indent
  \textbf{#1}
  \ 
  \textit{#2}
  \ 
  \hfill{}
  {#3}\vspace{1ex}}

% Table formatting
\newcommand{\cvtable}[1]{
  {\renewcommand{\arraystretch}{1.2}
    \begin{tabular}{p{\dimexpr.4\textwidth-1\parindent}p{\dimexpr.6\textwidth}}
      #1
    \end{tabular}}
}

% List formatting
\newcommand{\cvlist}[1]{
  \begin{itemize}[topsep=0ex,leftmargin=*,itemsep=0ex,parsep=1ex,labelwidth=\parindent]
    #1
  \end{itemize}
}

% ---------------------------------------------------------
% CV
% ---------------------------------------------------------

\begin{document}

% Footer
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{ \the\year }

% Name and links
\applicant{Alexander Rogachev}
\github{https://github.com/cog1to}
\email{sorryforbadname@gmail.com}
\skype{skype://rogachev.alex}
\location{Ivanovo, Russia}
\phone{+7-915-817-2792}

% Title
\maketitle

% Position
\cvsection{Position}
Mid/Senior iOS Developer

% Education
\cvsection{Education}
\cvparagraph{Ivanovo State University of Chemistry and Technology (ISUCT)}{}{2006 - 2012}
\begin{itemize}[topsep=0ex,leftmargin=*]
  \item M.S. Information Technology
\end{itemize}

% Experience
\cvsection{Work Experience}

\cvparagraph{Avito}{iOS Developer @ Messenger}{2019 - Present}
\cvlist{
  \item Participating in the architecture design \& development of a Messenger module of Avito iOS app [\href{https://apps.apple.com/ru/app/\%D0\%B0\%D0\%B2\%D0\%B8\%D1\%82\%D0\%BE-\%D0\%BE\%D0\%B1\%D1\%8A\%D1\%8F\%D0\%B2\%D0\%BB\%D0\%B5\%D0\%BD\%D0\%B8\%D1\%8F/id417281773}{link}], one of the top C2C trading platforms in Russia.
}
\vspace{1ex}

\cvparagraph{Akvelon}{Senior iOS Developer \& SDET}{2014 - Present}
\cvlist{
  \item Leading the development of an iOS client for Intapp product family [\href{https://itunes.apple.com/us/app/intapp/id1052877767}{link}], integrating multiple back-end services in a single mobile app.
  \item Maintaining and expanding API server code for one of the Intapp's products written in ASP.NET MVC.
  \item Developing and maintaning UI test automation solution for iOS and Android clients.
  \item Developed an in-house UI automation framework for Smartsheet iPhone and iPad apps [\href{https://itunes.apple.com/us/app/smartsheet/id568421135}{link}], including fixture server and CI with report gathering. Led the initial effort of automating existing test plans.
}
\vspace{1ex}

\cvparagraph{Akvelon}{Junior Mobile Developer \& SDET}{2010 - 2014}
\cvlist{
  \item Developed a camera control application for prototype Android devices with enhanced digital cameras and proprietary firmware.
  \item Developed an over-WiFi video streaming application for iOS devices based on UDP protocol and ffmpeg [\href{http://neuronbeta.com/chirpglobal/chirpvision/app/}{link}].
  \item Developed a UI test automation solution for LinkedIn iOS applications.
  \item Developed an iOS app for performing data copy and data backup via socket-based peer-to-peer connection between Android, iOS and Blackberry devices.
  \item Developed a marketing application for T-Mobile.
  \item Developed an Android activity-tracking application with Microsoft CRM integration.
}

% Skills
\cvsection{Skills}
\cvtable{
  \textbf{Main languages:} & Swift, Objective C \\
  \textbf{Secondary languages:} & Java, C\#, JS \\
  \textbf{Main platform:} & iOS \\
  \textbf{Frameworks/Libraries/Tools:} & MVC, MVP, MVVM, UIKit, CoreData, RxSwift, Realm, AFNetworking, Carthage, CocoaPods, Appium, XCTest, SQL, Bash, Git, Mercurial, Jira, Xcode, Instruments, ...
}

% Languages
\cvsection{Languages}
\cvtable{
  \textbf{Russian:} & Native \\
  \textbf{English:} & Advanced \\
}

\end{document}
